### 2016-04-25 ch03-lrm/nonparametric.tex
Lots of work on CH03

Whereas many areas of system identification focus on parametric identification and/or parameter estimation, non-parametric techniques have recently received renewed interest from the community.

\begin{itemize}
\item \TODO{explain non-parametric}
\item \TODO{explain why non-parametric is good}
\end{itemize}

The measurement of \glspl{FRF} of dynamic systems is an important step in many technical applications, often used as a simple visualization of the system dynamics.
\gls{FRF} measurement techniques are discussed, for instance, in
\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to practical devices and systems~\citep{Lim2010,Robinson1990,Behjat2010}, among others.
Besides, \glspl{FRF} have been shown to provide a quick insight into the dynamic properties of \gls{LTI} systems.
This capability is very useful for model validation and/or model selection~\citep{Pintelon2012}.

\input{\thisDir/lrm-paper.tex}

>>>>

Whereas many areas of system identification focus on parametric identification and/or parameter estimation, non-parametric techniques have recently received renewed interest from the community.
One of the reasons for this is that non-parametric techniques typically require less assumptions and knowledge of the system than building parametric models.
As a consequence, non-parametric methods are often more robust to wrong assumptions than fully parametric methods.
Besides, \glspl{FRF} have been shown to provide a quick insight into the basic dynamic properties of \gls{LTI} systems.
This capability is very useful for system design, controller design, model validation and model selection for parametric models~\citep{Pintelon2012}.

The measurement of \glspl{FRF} of dynamic systems is an important step in many technical applications, often used as a simple visualization of the system dynamics.
However, obtaining a good non-parametric \gls{FRF} from a measured input-output data set can prove difficult due to the presence of noise, leakage and measurement time limitations to observe lightly-damped dynamics well.
\gls{FRF} measurement techniques are discussed, for instance, in
\citep{Schoukens1998,Schoukens2006LPM,Guillaume1996,Broersen1995,Pintelon2010LPM1,Antoni2007FRF,Pintelon2012}, and applied to practical devices and systems~\citep{Lim2010,Robinson1990,Behjat2010}, among others.

In this chapter, we will investigate local modeling techniques to capture the \gls{FRF} of resonant systems.
In particular, a comparison between the \gls{LPM} and \gls{LRM} will be made such that it can be decided which method is to be preferred over the other in what conditions of \gls{SNR} and frequency resolution (or, equivalently, measurement time).

\paragraph*{Outline}
\secref{sec:theory} introduces theory of estimating \glspl{FRF} using local modeling techniques.
In \secref{sec:biascalc}, the bias of the \gls{LRM} is derived.
In \secref{sec:simulations} the performance of the different modeling methods are compared by means of simulations.
In \secref{sec:nparam:orderSelection}, some options for model order selection are discussed.
In \secref{sec:nonparametric:truncation}, an approach is developed to further reduce the variance of the \gls{LPM} estimate by truncation of the impulse response.
Finally, conclusions are presented in \secref{sec:conclusion}.

\section{Local modeling approaches}
\label{sec:theory}

Consider a discrete-time generalized output-error \gls{LTI} set-up, excited by the input signal $u[n]$.
For an infinite data length, such a system can be described in the time domain by
\begin{equation}
  y[n] = \ezbrace{\true{G}(z) u[n]}{\true{y}[n]} + \ezbrace{\true{H}(z) \true{e}[n]}{v[n]} \text{ with } n \in \IntegerNumbers
  \label{eq:output-error-TD-infinite}
\end{equation}
where $v[n]$ is filtered white noise, $v[n] = \true{H}(z) \true{e}[n]$ where $z^{-1}$ is the backward shift operator, i.e. $z^ {-1}x[n] = x[n-1]$.
The transfer functions $\true{G}$ and $\true{H}$ are rational functions that are stable and causal.

During typical measurements, however, $y[n]$ and $u[n]$ are only measured over a limited time span, i.e. $n \in \set{0,1,\ldots,N-1}$.
This introduces transient terms $t_{\bullet}$ in this relationship~\citep{Pintelon1997ARB}:
\begin{equation}
y[n] = \true{G}(z) u[n] + \true{H}(z) \true{e}[n] + \ezbrace{t_G[n] + t_H[n]}{t[n]}
\label{eq:output-error-TD-finite}
\end{equation}
where $t_G[n]$ and $t_H[n]$ are due to the different conditions of respectively $\true{G}$ and $\true{H}$ at the beginning and end of the measurement record~\citep{Pintelon1997ARB}.
Both terms can be lumped together as $t[n]$, which is often~\citep{Pintelon2010LPM1} determined predominantly by $t_G[n]$.

\begin{definition}\label{def:DFT}
The $N$-points \glsfirst{DFT} of a signal $x(n\Ts) = x[n]$ with $n \in \set{0,\ldots,N-1}$ is
\begin{equation}
  X \left[ k \right] =
  X \left( \omega_k \right)
  \isdef
  \frac{1}{\sqrt{N}}\sum_{n=0}^{N-1} x \left( n \Ts \right)  \exponent{- j \omega_k n \Ts }
  \label{eq:DFT}
\end{equation}
where $\omega_k \isdef \tfrac{2 \pi k }{N \Ts}$, $k \in \set{0,\ldots,N-1}$ and $\Ts$ is the sampling time.
\end{definition}

By applying the \gls{DFT}~\eqref{eq:DFT} to both sides of \eqref{eq:output-error-TD-finite}, one obtains its frequency-domain counterpart:
\begin{align}
    Y \left( \omega_k \right) 
    & = \true{G} \left( \omega_k \right) U \left( \omega_k \right) 
      + \true{H} \left( \omega_k \right) E \left( \omega_k \right)
      + T \left( \omega_k \right)\\
      &= \true{G} \left( \omega_k \right) U \left( \omega_k \right)  + V(\omega_k) + T(\omega_k)
      \text{.}
  \label{eq:output-error-FD}
\end{align}

Here, we focus on using local modeling to separate the different terms, i.e.
\begin{itemize}
  \item the transfer function $\true{G}$,
  \item the leakage term $T$, and
  \item the noise term $V$.
\end{itemize}
The main term of interest, however, is the transfer function $\true{G}$ and a secondary concern is estimating the noise variance $\Var{V}$.

\subsection{Local modeling}
Local modeling methods  exploit the `smoothness' (or conversely `roughness') of the different terms of \eqref{eq:output-error-FD} over the frequency $\omega$.
In particular, we will assume that $U(\omega)$ is `rough' over the frequency~\citep{Schoukens2009LPM}, e.g. as is the case for noise excitations or random phase multisines (see further).
On the other hand, it is well-known that the transfer functions $\true{G}$, $\true{H}$ and hence also the corresponding transient contributions $T = T_G + T_H$ are smooth over the frequency.
As such, these smooth contributions can be approximated well around each frequency $\omega_k$ using a local rational model:
\begin{align}
  \true{G}(\omega_{k}+d) 
  &\approx
  \frac{\Sum_{i=0}^{\order{B}} b_i d^i}
            {1 + \Sum_{i=1}^{\order{A}} a_i d^i}
    &\isdef
    \frac{\LocalModel[k]{B}(d)}%
           {\LocalModel[k]{A}(d)} 
           = \LocalModel[k]{G}(d)
  \text{,}
  \label{eq:LRM:model:G}
  \\
  \true{T}(\omega_k + d) &\approx
  \frac{\Sum_{i=0}^{\order{C}} c_i d^i}
            {1 + \Sum_{i=1}^{\order{A}} a_i d^i}
    &\isdef 
      \frac{\LocalModel[k]{C}(d)}%
           {\LocalModel[k]{A}(d)}
      = \LocalModel[k]{T}(d)
  \text{.}
  \label{eq:LRM:model:T}
\end{align}

In these expressions, we denote $\LocalModel[k]{G}$ and $\LocalModel[k]{T}$ for the local model for respectively transfer function and the transient.
Note that such local quantities (which depend on the frequency bin $k$) are denoted in bold.
To alleviate the notations, the subscript $k$ is omitted unless

The local parameters $\theta$  
\begin{equation}
\theta \isdef 
\begin{bmatrix}
\theta_A\\ 
\theta_B\\
\theta_C
\end{bmatrix}
\qquad \text{ with }
\theta_A \isdef
\begin{bmatrix}
a_1\\ \vdots\\ a_{\order{A}}
\end{bmatrix}
\text{, }
\theta_B \isdef
\begin{bmatrix}
b_0\\ \vdots\\ b_{\order{B}}
\end{bmatrix}
\text{, and }
\theta_C \isdef
\begin{bmatrix}
c_0\\ \vdots\\ c_{\order{C}}
\end{bmatrix}
\end{equation}
in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}, we consider a local window
\begin{equation}
  \LocalWindow[k] 
  \isdef
  \Set{
    \omega_{k+r} 
    | 
    r \in \LocalShifts{k}
  }
\end{equation}
with $\LocalShifts{k} \isdef \Set{-\numel{W}, -\numel{W}+1, \ldots, 0, \ldots, \numel{W}}$
such that the local window around $\omega_k$ consists of $\numel{\LocalWindow} = 2 \numel{W} + 1$ bins. 
If one denotes the input/output spectra in such a local frequency window $\LocalWindow[k]$ as
\begin{equation}
  \LocalVector{U}_k \isdef 
  \mat{
    U(\omega_{k-\numel{W}})\\
    \vdots\\
    U(\omega_{k})\\
    \vdots\\
    U(\omega_{k+\numel{W}})\\
  }
  \text{ and }
  \LocalVector{Y}_k \isdef 
  \mat{
    Y(\omega_{k-\numel{W}})\\
    \vdots\\
    Y(\omega_{k})\\
    \vdots\\
    Y(\omega_{k+\numel{W}})\\
  }
  \text{,}
\end{equation}
and similarly for the other quantities, equation \eqref{eq:output-error-FD} limited to $\LocalWindow[k]$ can be written as
\begin{equation}
  \LocalVector{Y}_k  = {\true{\LocalVector{G}}}_k \hadamard \LocalVector{U}_k + \LocalVector{T}_k + \LocalVector{V}_k
\text{,}
\end{equation} 
where $\hadamard$ denotes the element-wise product (also, Hadamard product).
Substituting $\true{\LocalVector{G}}$ and $\LocalVector{T}$ with the local models $\LocalModel{G}$ and $\LocalModel{T}$ and neglecting the influence of $\LocalVector{V}$ yields
\begin{equation}
  \LocalVector{Y} 
  \approx 
  \hat{\LocalVector{Y}} 
    =
      \LocalModel{G} \hadamard \LocalVector{U} + \LocalModel{T}
      \text{.}
      \label{eq:local-system-equations}
\end{equation}
Note that this encompasses $\nWind$ complex equations in the $\nth = \order{A} + \order{B} + \order{C} + 2$  unknown complex model parameters ($a_i$, $b_i$ and $c_i$ in \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}).
Consequently, a necessary condition to compute the model parameters is that
\begin{equation}
  \DOF = \nWind - \nth
       = 2 \numel{W} - \order{A} - \order{B} - \order{C} - 1
\end{equation}
is positive.
To effectively compute the local model parameters, the equation error in \eqref{eq:local-system-equations} is minimized by formulating a quadratic cost function:
\begin{equation}
  \LocalVector{\CostFunc{\LRIC}} 
    \isdef 
      \left( \LocalVector{Y}  -  \LocalModel{G} \hadamard \LocalVector{U} - \LocalModel{T} \right)^{\HT} 
      \left( \LocalVector{Y}  -  \LocalModel{G} \hadamard \LocalVector{U} - \LocalModel{T} \right)
   \label{eq:costfunc:LRIC}
   \text{.}
\end{equation}
Due to the presence of the denominator of $\LocalModel{G} = \frac{\LocalModel{B}}{\LocalModel{A}}$, the equation error is not linear in the parameters $a_i$ and hence \eqref{eq:costfunc:LRIC} requires starting values and time-consuming iterative optimization schemes to obtain a parameter estimate.
We denote such a method as $\lric{\numel{W},\order{B},\order{A},\order{C}}$.

\subsection{The Local Rational Method}
\label{sec:nparam:LRM}
The \gls{LRM} as first introduced in \citet{McKelvey2012LRM}, overcomes the computational burden of an iterative procedure by weighting the equation error by the denominator polynomial $\LocalModel{A}$  akin to the procedure in \citep{Levy1959}.
I.e. the \gls{LRM} procedure tries to minimize the equation error in
\begin{equation}
  \LocalModel{A} \hadamard \LocalVector{Y} = \LocalModel{B} \hadamard \LocalVector{U}  + \LocalVector{C} + \LocalVector{V}
  \text{,}
\end{equation}
for which the corresponding cost function is
\begin{equation}
  \LocalVector{\CostFunc{\LRM}}
  \isdef 
  \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)^{\HT} 
      \left( \LocalModel{A} \hadamard \LocalVector{Y}  -  \LocalModel{B} \hadamard \LocalVector{U} - \LocalModel{C} \right)
      \text{.}
      \label{eq:nparam:LRM:costFunc}
\end{equation}
where $\LocalVector{V}$ is vector consisting of \gls{iid} complex normally distributed variables~\citep{Gallager2008} that each have a variance $\sigma_V^2$, i.e. the disturbing noise is assumed white over the local frequency window.
Equivalently, the last equation can be rewritten as a linear regression problem
\begin{equation}
  \LocalVector{Y} = \LocalMatrix{K} \LocalVector{\theta} + \LocalVector{V}
\end{equation}
where $\LocalMatrix{K}$ is the so-called design matrix (or observation matrix):
\begin{align}
  \label{eq:nparam:designMatrix}
  \LocalMatrix{K} 
    & \isdef 
  \mat{
     \LocalMatrix{K}_A &
     \LocalMatrix{K}_B & 
     \LocalMatrix{K}_C
  }\\
  \LocalMatrix{K}_A 
    &\isdef
    \mat{
      \LocalVector{Y} \hadamard \LocalVector{d}^1 &
      \cdots &
      \LocalVector{Y} \hadamard \LocalVector{d}^{\order{A}}
    }\\
  \LocalMatrix{K}_B 
    &\isdef
    \mat{
      \LocalVector{U} \hadamard \LocalVector{d}^0 &
      \cdots &
      \LocalVector{U} \hadamard \LocalVector{d}^{\order{B}}
    }\\
  \LocalMatrix{K}_C
    &\isdef
    \mat{
      \LocalVector{d}^0 &
      \cdots &
      \LocalVector{d}^{\order{C}}
    }
    \text{.}
\end{align}
In this formulation, we have used $\LocalVector{d}^{n}$ to denote the $n^{\text{th}}$ Hadamard power of $\LocalVector{d}$ (this corresponds to \mcode{d.^n} in \MATLAB) such that
\begin{equation}
    \LocalVector{d}^{n} 
    \isdef
    \mat{
      (-\numel{W})^{n} &
      \cdots &
      (\numel{W})^{n}
    }^{\T}
    \text{ with $n \in \mathbb{Z}$}
\end{equation}
where every element corresponds to a value of $d^{n}$ in accordance with $\LocalShifts{k}$.

This formulation facilitates to solve the problem in a one-step approach:
\begin{equation}
  \LocalVector{\theta}_{\LRM} 
    \isdef \pinv{\LocalMatrix{K}} \LocalVector{Y}
    = \KTK{\LocalMatrix{K}} \LocalVector{Y}
    \label{eq:nparam:LRM:normalEquations}
\end{equation}
where $\pinv{\LocalMatrix{K}}$ denotes the Moore-Penroose pseudo-inverse of $\LocalMatrix{K}$.

\TODO{hier voortschrijven: ruisvariantie berekenen}

\begin{remark}
This system can only be solved reliably if the columns in \eqref{eq:nparam:designMatrix} are linearly independent.
In practice, this corresponds to the requirements on the input spectrum as stated in \citet{Schoukens2009LPM}: the input spectrum should be sufficiently `rough' to separate the transient contribution.
This can be obtained e.g. using random phase multisines or random input signals.
\end{remark}

\begin{remark}
Since it is well-known that the Vandemonde structure in the design matrix \eqref{eq:nparam:designMatrix} leads to numerical ill-conditioning for higher model complexities, additional measures are taken to improve numerical conditioning.
To improve numerical conditioning~\citep{Pintelon2005} of the estimation problem, we substitute $d = \dw{r}{k}$ in equations \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T}
\begin{equation}
\dw{r}{k} \isdef \frac{\omega_{k+r} - \omega_k}{\Delta \omega_k}
\label{eq:freqScaling}
\end{equation}
where
\begin{equation}
  \Delta \omega_k \isdef
  \max
  \Set{
    \abs{ \omega_k - \omega_j} |  \vphantom{\frac{a}{b}}  \omega_j \in \LocalWindow[k]
  }
\end{equation}
such that $\abs{\dw{r}{k}} \leq 1$ when $r \in \LocalShifts{k}$.
\end{remark}

We denote a method that solves \eqref{eq:nparam:LRM:costFunc} for given bandwidth and local orders as $\lrm{\numel{W}, \order{B},\order{A},\order{C}}$.

\subsection{The Local Polynomial Method}
The \gls{LPM} is method that predates the \gls{LRM} and has been devised by~\citet{Schoukens2006LPM}.
The \gls{LPM} approximates both the \gls{FRF} and transient contribution by means of complex-valued local polynomials in the frequency domain.

The \gls{LPM} can be understood as a specific case of the \gls{LRM}: for  $\order{A} = 0$, the \gls{LRM} reduces to the \gls{LPM}.
As such, we can use the notation $\lpm{\numel{W}, \order{B}, \order{C}}$ as a synonym for $\lrm{\nWind, 0, \order{C}}$.

\begin{remark}
The trivial setting for local `modeling' where a window with a total width of $1\unit{bin}$ and no transient estimation ($\order{C} = -1$), actually corresponds to the simple \gls{ETFE}~\citep{Broersen1995,Stenman2000ASETFE,Stenman2001ASFRF} when no further smoothing or windowing is applied:
\begin{equation}
  \estimated{G}_{\ETFE}(\omega_k) \isdef \frac{Y(\omega_k)}{U(\omega_k)}
  \label{eq:nparam:ETFE}
\end{equation}
As such, $\ETFE \equiv \lrm{0,0,0,-1} \equiv \lpm{0,0,-1}$.
\end{remark}

\begin{remark}
The methods proposed by \citet{Stenman2001ASFRF,Stenman2000ASETFE} also refer to `local polynomial regression' to smoothen the \gls{FRF}.
It should be noted, however, that such methods differ significantly from the \gls{LPM}.
Specifically, those methods operate directly on the raw \gls{ETFE}, in contrast to the \gls{LPM} which uses the input-output spectra and can hence estimate both an \gls{FRF} and a transient contribution.
Moreover, the methods proposed by \citet{Stenman2001ASFRF} build upon `local regression` approaches such as \gls{LOWESS}.
See e.g. \citet{Loader1999} for more information regarding these `local regression' approaches.
\end{remark}

\section{Derivation of the Bias of the \glsentrytext{LRM}}
\label{sec:biascalc}
Since the local design matrix \eqref{eq:nparam:designMatrix} of the \gls{LRM} contains the noisy output spectrum $\LocalVector{Y}$ when $\order{A} > 0$, the \gls{LRM} is expected to be a biased estimator.
In this section, we will derive expressions for the bias such that it can be quantified how important this bias is in different situations.

To determine the bias, an approach similar to \citep[Appendix A]{Guillaume1995} is followed.
Let us denote the expected value of the cost function over all measurements $\LocalVector{Z} = \mat{\LocalMatrix{Y}, \LocalMatrix{U}}$ as
\begin{align}
  \ELSCost{\theta}
              & \isdef 
                   \E[\LocalVector{Z}]%
                         {    
                                \LSCost{\LocalVector{\theta}, \LocalVector{Z}}} \\
              & = \ELSCost[0]{\theta} + \ELSCost[n]{\theta} \\
    \ELSCost[0]{\theta} & \isdef 
            \frac{1}{\nWind} 
                \sum_{\dW} 
                     \left| 
                             \LocalModel{A}(\dW, \LocalVector{\theta}) \true{\LocalVector{Y}}
                          - \LocalModel{B}(\dW, \LocalVector{\theta}) \true{\LocalVector{U}}
                          - \LocalModel{C}(\dW, \LocalVector{\theta}) 
                    \right|^2 \\
    \ELSCost[n]{\theta} & \isdef 
              \frac{1}{\nWind} 
                     \sum_{\dW} 
                              \left| \LocalModel{A}(\dW,\LocalVector{\theta}) \right|^2 
                              \sigma_V^2
\end{align}
where $\true{\LocalVector{U}}$ and $\true{\LocalVector{Y}}$ denote the `true' (noiseless) input-output spectra in the local window.
Note that this function is a quadratic function of $\LocalVector{\theta}$ and hence it can be represented exactly by its second order Taylor series around $\true\theta$:
\begin{multline}
  \ELSCost{\theta} = \ELSCost{\true\theta} 
  + \PartialDerivative{\ELSCost{\true\theta}}{\true\theta}  \left( \theta - \true\theta \right) %\\
  + \frac{1}{2} \left( \theta - \true\theta \right)^{\T} 
  \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} 
   \left( \theta - \true\theta \right)
   \text{.}
\end{multline}
The minimizer $\estimated\theta$ of this function can be obtained by equating the derivative
\begin{equation}
  \PartialDerivative{\ELSCost{\estimated\theta}}
                                          {\estimated\theta} 
  = 
  \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T} 
  + \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \left( \estimated\theta - \true\theta \right)
\end{equation}
to zero.
This is equivalent to 
\begin{equation}
  \left( \estimated\theta - \true\theta \right) 
  = 
  - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta} \right)^{-1}  
     \left( \PartialDerivative{\ELSCost{\true\theta}}{\true\theta} \right)^{\T}
  \text{.}
\end{equation}
which expresses the bias $\Delta\theta = \left( \estimated\theta - \true\theta \right)$ of the estimated parameters.
Remark that 
\begin{equation}
  \PartialDerivative{\ELSCost{\true\theta}}{\true\theta}  
  = 
  \PartialDerivative{\ELSCost[0]{\theta} + \ELSCost[n]{\theta} }{\true\theta} 
  = 
  \PartialDerivative{\ELSCost[n]{\theta} }{\true\theta} 
\end{equation}
since $\ELSCost[0]{\theta}$ is minimized in $\true\theta$ by definition.
As such, the bias on the parameters can be simplified to
\begin{equation}
  \Delta\theta = 
  - \left(   \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta^2} \right)^{-1} 
     \left( \PartialDerivative{\ELSCost[n]{\true\theta}}{\true\theta} \right)^{\T}
  \text{.}
  \label{eq:nparam:bias-basic}
\end{equation}

Do note that the estimated parameters $\theta \in \ComplexMatrix{\nth \times 1}$ but that $\ELSCost{\theta}$ is a real-valued function.
In contrast to a complex-valued function, this requires additional attention when the derivatives are calculated~\citep{Messerschmitt2006} and~\citep[Section 15.9]{Pintelon2012} since $\ELSCost{\theta}$ is not an analytic function.
Particularly, the function $\ELSCost{\theta}$ is regarded as a two-dimensional function $\ELSCost{\theta,\conj{\theta}}$ where $\conj{\theta}$ and $\theta$ are considered as independent variables~\citep{Hjorungnes2007,Hjorungnes2011}.
The derivatives are then computed with respect to these variables.

To facilitate the derivations, we rewrite the expected value of the cost function in terms of $\theta$ and $\conj{\theta}$:
\begin{align}
   \ELSCost[0]{\theta,\conj{\theta}} & =
      \frac{1}{\nWind}
           \sum_{\dW}
           \LocalModel{Q}(      \dW,        \LocalVector{\theta},  \true{      \LocalVector{Y}},  \true{      \LocalVector{U} })
           \LocalModel{Q}(\conj{\dW}, \conj{\LocalVector{\theta}}, \true{\conj{\LocalVector{Y}}}, \true{\conj{\LocalVector{U}}})
   \\
   \LocalModel{Q}(\dW, \LocalVector{\theta},  \true{\LocalVector{Y}},  \true{ \LocalVector{U} }) & \isdef
                 \LocalModel{A}(\dW, \LocalVector{\theta}) \true{\LocalVector{Y}}(\dW)
               - \LocalModel{B}(\dW, \LocalVector{\theta}) \true{\LocalVector{U}}(\dW)
               - \LocalModel{C}(\dW, \LocalVector{\theta})
    \\             
    \ELSCost[n]{\theta,\conj{\theta}} & =
              \frac{\sigma_V^2}{\nWind} 
                     \sum_{r} 
                               \LocalModel{A}(      \dW,        \LocalVector{\theta} ) 
                               \LocalModel{A}(\conj{\dW}, \conj{\LocalVector{\theta}}) 
\end{align}
since $\conj{ \LocalModel{A}(\dW,\theta)} =  \LocalModel{A}(\conj{\dW},\conj{\theta}) $, and similar for $\LocalModel{B}$ and $\LocalModel{C}$ and $\LocalModel{Q}$.

\paragraph{Contributions to the first order derivative}
The last term in \eqref{eq:nparam:bias-basic}, i.e. the first order derivative,  is given by
\begin{equation}
  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta}
  = 
  \begin{bmatrix}
  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_A} &
  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_B} &
  \PartialDerivative{\ELSCost[0]{\true\theta, \conj{\true\theta}}}{\theta_C}
  \end{bmatrix}
\end{equation}
and split into the parts pertaining to respectively $\LocalModel{A}$, $\LocalModel{B}$ and, $\LocalModel{C}$.
The respective components are given by:
\begin{align}
  \PartialDerivative{\ELSCost[n]{\theta,\conj{\theta}}}{a_i} 
     &= 
     \frac{\sigma_V^2}{\nWind}
     \sum_{\dW} \dW^i \LocalModel{A}(\conj{\dW},\conj{\LocalVector{\theta}}) 
     && \forall i \in \set{1,\ldots,\order{A}}
     \\
   \PartialDerivative{\ELSCost[n]{\theta,\conj{\theta}}}{b_i} 
   &= 0
   && \forall i \in \set{0,\ldots,\order{B}}
   \\
   \PartialDerivative{\ELSCost[n]{\theta,\conj{\theta}}}{c_i} 
   &= 0
   &&\forall i \in \set{0,\ldots,\order{C}}
   \text{.}
\end{align}
It can be seen that only the factors pertaining to $\theta_{A}$ are present.
As this term occurs linearly in expression \eqref{eq:nparam:bias-basic}, only $\theta_A$ can incur a bias.
Consequently, only the poles can shifted by the presence of noise.
As such, the bias term $\Delta \theta$ can be written in the following sparse form:
\begin{equation}
  \Delta \theta = 
  \begin{bmatrix}
    \Delta \theta_A\\
    \Delta \theta_B\\
    \Delta \theta_C
  \end{bmatrix}
  =
  \begin{bmatrix}
    \Delta \theta_A\\
    \deemph{0}\\
    \deemph{0}
  \end{bmatrix}
  \text{.}
  \label{eq:nparam:lrm:bias:sparse}
\end{equation}

\paragraph{Contributions to the Hessian}
Computing the Hessian in \eqref{eq:nparam:bias-basic} also boils down to recognizing the block structure.
This results in the following block matrix:
\begin{equation}
  \PartialDerivative[2]{\ELSCost{\true\theta}}{\true\theta^2} =
  \begin{bmatrix}
    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_A } &
    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_A } & 
    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_A } \\
    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_B } &
    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_B } & 
    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_B } \\
    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_C } &
    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_C } & 
    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_C }
  \end{bmatrix}
  \label{eq:nparam:lrm:bias:hessian}
\end{equation}
where every sub-block consists of the different second-order derivatives and exhibits a similar pattern.

The different contributions are given below:
\begin{align}
  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{a_{i_1}} \pd a_{i_2}} & = 
  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \abs{\true{\LocalVector{Y}}(\dW)}^2\\
  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{b_{i_1}} \pd b_{i_2}} & = 
  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \abs{\true{\LocalVector{U}}(\dW)}^2\\
  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{c_{i_1}} \pd c_{i_2}} & = 
  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2}\\
  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{b_{i_1}} \pd a_{i_2}}  =
  \conj{ \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{a_{i_2}} \pd b_{i_1}} }& = 
  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \conj{\true{\LocalVector{U}}(\dW)} \true{\LocalVector{Y}}(\dW)\\
  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{c_{i_1}} \pd a_{i_2}}  =
  \conj{ \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{a_{i_2}} \pd c_{i_1}} }& = 
  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \true{\LocalVector{Y}}(\dW)\\
  \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{c_{i_1}} \pd b_{i_2}}  =
  \conj{ \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{c_{i_2}} \pd b_{i_1}} }& = 
  \frac{1}{\nWind} \sum_{\dW} \dW^{i_1+i_2} \true{\LocalVector{U}}(\dW)
  \text{.}
\end{align}

\begin{remark}
Computing the inverse of this Hessian cannot, to the knowledge of the author, be reduced to a form that yields more insight.
However, if the non-diagonal blocks can be neglected, this would lead to an inverse that is also block-diagonal:
\begin{equation}
   \begin{bmatrix}
    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_A } &
    \deemph{0} & 
    \deemph{0} \\
    \deemph{0} &
    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_B } & 
    \deemph{0} \\
    \deemph{0} &
    \deemph{0} & 
    \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_C }
  \end{bmatrix}^{-1}
  \!\!\!=
  \begin{bmatrix}
    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_A \pd \theta_A }\right)^{-1} &
    \deemph{0} & 
    \deemph{0} \\
    \deemph{0} &
    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_B \pd \theta_B }\right)^{-1} & 
    \deemph{0} \\
    \deemph{0} &
    \deemph{0} & 
    \left( \PartialDerivative[2]{\ELSCost{\theta}}{ \conj{\theta}_C \pd \theta_C }\right)^{-1}
  \end{bmatrix}
  % \text{.}
\end{equation}
\end{remark}
\paragraph{Bias on the \glsentrydesc{FRF}}
As a first order approximation, the bias on the \gls{FRF} can be written as
\begin{equation}
  \Delta \LocalModel{G}(\omega_k) 
  =
  \Delta \LocalModel{G}(\dw{0}{k}) 
     \approx 
        \PartialDerivative{\LocalModel{G}(\theta, \dw{0}{k})}
                                          {\theta} 
      \Delta \theta
      \text{.}
\end{equation}
The derivative in that expression can be evaluated easily
\begin{align}
    \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta} 
     &=
     \begin{bmatrix}
       \PartialDerivative{\LocalModel{G}(\theta,\dW)}{\theta_A} &
       \PartialDerivative{\LocalModel{G}(\theta,\dW)}{\theta_B} &
       \PartialDerivative{\LocalModel{G}(\theta,\dW)}{\theta_C} 
     \end{bmatrix}
     \\
     \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta_A} 
     &=
     - \frac{\LocalModel{B}(\theta, r)}{\LocalModel{A}^2(\theta, r)}
     \begin{bmatrix}
         \dW^1 & \dW^2 & \deemph{\cdots} & \dW^{\order{A}}
     \end{bmatrix}
     \\
     \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta_B} 
     &=
     \frac{1}{\LocalModel{A}(\theta, \dW)}
     \begin{bmatrix}
         1 & \dW^1 & \dW^2 & \deemph{\cdots} & \dW^{\order{B}}
     \end{bmatrix}
     \\
     \PartialDerivative{\LocalModel{G}(\theta, \dW)}{\theta_C} 
     &=
     \Zero{1 \times \order{C}+1}
     \text{.}
\end{align}

However, the sparsity of $\Delta\theta$, see \eqref{eq:nparam:lrm:bias:sparse}, can be exploited such that the bias on the \gls{FRF} can be expressed as:
\begin{equation}
  \Delta \LocalModel{G}(\theta,\dW)
  \approx
  \frac{\LocalModel{G}(\theta, \dW)}
           {\LocalModel{A}(\theta, \dW)}
  \begin{bmatrix}
    \dW^1 & \deemph{\cdots} & \dW^{\order{A}}
  \end{bmatrix}
  \Delta \theta_A
  \text{.}
\end{equation}
Equivalently, the relative bias of the \gls{FRF} can be written as
\begin{equation}
\frac{\Delta \LocalModel{G}(\theta,\dW)}{\LocalModel{G}(\theta,\dW)}
\approx
\LocalModel{A}(\theta,\dW)^{-1}
\begin{bmatrix}
    \dW^1 & \deemph{\cdots} & \dW^{\order{A}}
  \end{bmatrix}
  \left(  \PartialDerivative[2]{\ELSCost{\theta}}{ \theta^2 } \right)^{-1}
  \begin{bmatrix}
  \Delta\theta_A\\
  0\\
  0\\
  \end{bmatrix}
  \text{.}
\end{equation}

\section{Simulations}
\label{sec:simulations}
